Universal Anonymous Signatures

### 2022-10-07 prism-backend/research/gsac/app-uas-proofs.tex
Last minute typo fixing.

  From an adversary \adv~against game 2, we can build an adversary \advB against
  \SBCM's blindness property. The simulation that \advB does is straightforward.
  \advB runs game 2 for \adv, using the \SBCM \parm variable it receives, to
  set up the \SBCM instance for game 2. When \adv~makes a query to its \OBTCHALb
  oracle, \advB prepares a call to its $\oracle{BLIND}^\RelIss$ oracle, setting
  $\osmsg_b \gets \PRVUK[\cuid_b]$ as message to be blindly signed and
  accompanying each $\osmsg_b$ with its corresponding
  $(\cscid_{i,b},\ATTR[\cscid_{i,b}])$ (for all $i\in[n]$). In the response
  received from $\oracle{BLIND}^\RelIss$ (which succeeds in case both options
  are in \RelIss), \advB replaces the proof with a simulated one, and \yissue
  with a random value (as done in game 2). With the response from \adv, \advB
  completes the credential running \SBCMUnblind as usual. The rest of the
  simulation is as in game 2. Finally, \advB outputs whatever \adv~outputs.
  Again, zero-knowledge of the NIZK for \RelIss, and the fact that \fissue is
  \UAS-acceptable, ensure that simulation is correct, and \advB wins whenever
  \adv~does.
  %
  \qed
\end{proof}

>>>>

  From an adversary \adv~against game 2, we can build an adversary \advB against
  \SBCM's blindness property. The simulation that \advB does is straightforward.
  \advB runs game 2 for \adv, using the \SBCM \parm variable it receives, to
  set up the \SBCM instance for game 2. When \adv~makes a query to its \OBTCHALb
  oracle, \advB prepares a call to its $\oracle{BLIND}^{\RelIss}$ oracle, setting
  $\osmsg_b \gets \PRVUK[\cuid_b]$ as message to be blindly signed and
  accompanying each $\osmsg_b$ with its corresponding
  $(\cscid_{i,b},\ATTR[\cscid_{i,b}])$ (for all $i\in[n]$). In the response
  received from $\oracle{BLIND}^{\RelIss}$ (which succeeds in case both options
  are in \RelIss), \advB replaces the proof with a simulated one, and \yissue
  with a random value (as done in game 2). With the response from \adv, \advB
  completes the credential running \SBCMUnblind as usual. The rest of the
  simulation is as in game 2. Finally, \advB outputs whatever \adv~outputs.
  Again, zero-knowledge of the NIZK for \RelIss, and the fact that \fissue is
  \UAS-acceptable, ensure that simulation is correct, and \advB wins whenever
  \adv~does.
  %
  \qed
\end{proof}

### 2022-10-07 prism-backend/research/gsac/introduction-paper.tex
Last minute typo fixing.

But the flexibility obtained from combining models from the AC and GS
domains into one also brings complexity. For instance, in order to meet
the general practice in AC, our UAS model includes multiple issuers. Along with
the combination of GS features, this paves the way to including multiple
openers, each with its own opening functionality. While powerful from a
practical point of view, this introduces similar (unavoidable?) limitations
privacy-wise as in functional encryption schemes \cite{bsw11} -- e.g., revealing
too granular information at signing or opening time reduces privacy. However, on
this occasion, signers control ``how deanonymisable'' their signatures will
be, and know it at signature generation time. This flexibility on the opening
values also leads to the need of using extraction-based techniques for the
modelling, since we cannot expect that opening outputs the real identity of the
signer. This is no surprise, though, as it was already observed in GS schemes
with non-conventional opening \cite{dl21}, in DAA schemes \cite{cdl16,cdl16b}.
In fact, simulation-extractability seems to be most useful here, something that
was also observed in \cite{cl06} for producing signatures out of knowledge of
witnesses for concrete NP statements.

>>>>

But the flexibility obtained from combining models from the AC and GS
domains into one also brings complexity. For instance, in order to meet
the general practice in AC, our UAS model includes multiple issuers. Along with
the combination of GS features, this paves the way to including multiple
openers, each with its own opening functionality. While powerful from a
practical point of view, this introduces similar (unavoidable?) limitations
privacy-wise as in functional encryption schemes \cite{bsw11} -- e.g., revealing
too granular information at signing or opening time reduces privacy. However, on
this occasion, signers control ``how deanonymisable'' their signatures will
be, and know it at signature generation time. This flexibility on the opening
values also leads to the need of using extraction-based techniques for the
modelling, since we cannot expect that opening outputs the real identity of the
signer. This is no surprise, though, as it was already observed in GS schemes
with non-conventional opening \cite{dl21}, and DAA schemes \cite{cdl16,cdl16b}.
In fact, simulation extractability seems to be most useful here, something that
was also observed in \cite{cl06} for producing signatures out of knowledge of
witnesses for concrete NP statements.

### 2022-10-07 prism-backend/research/gsac/preliminaries-paper.tex
Last minute typo fixing.

\paragraph{Public-Key Encryption.} %
Defined as a tuple (\ESetup,\EKeyGen,\EEnc,\EDec). Algorithm $\parm \gets
\ESetup(\secpar)$ produces public parameters for the other algorithms.
$(\ek,\dk) \gets \EKeyGen(\parm)$ generates the encryption-decryption key
pair, algorithm $\Ec \gets \EEnc(\ek,\msg)$ encrypts message \msg with
encryption key \ek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\dk,
\Ec)$ decrypts ciphertexts using decryption key \Edk. We rely on IND-CCA
public-key encryption schemes.

@@

\paragraph{Non-Interactive Zero-Knowledge.} %
We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
model. Informally, a NIZK scheme over an NP relation \NIZKRel is defined as a
tuple ($\NIZKSetupRel$,$\NIZKProveRel$,$\NIZKVerify^\NIZKRel$).
Algorithm $\NIZKcrs \gets \NIZKSetupRel(\secpar)$ produces the common
reference string \NIZKcrs. $\NIZKproof/\bot \gets \NIZKProveRel(\NIZKcrs,
\NIZKx,\NIZKw)$ creates a NIZK proof of knowledge of witness \NIZKw for \NIZKx
such that $(\NIZKw,\NIZKx) \in \NIZKRel$. $1/0 \gets \NIZKVerifyRel
(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof. Within NIZK systems, we
further need schemes that provide simulation-extractability, which in a nutshell
means that no adversary can produce a proof from which we cannot extract a
witness, even after seeing polynomially many simulated proofs. To model
simulation-extractable NIZKs, we further need algorithms \NIZKSimSetup,
\NIZKSim, and \NIZKExtract, that allow simulating proofs and extracting
witnesses. The properties we build on are completeness, soundness,
zero-knowledgeness, and simulation-extractability.

>>>>

\paragraph{Public-Key Encryption.} %
Defined as a tuple (\ESetup,\EKeyGen,\EEnc,\EDec). Algorithm $\parm \gets
\ESetup(\secpar)$ produces public parameters for the other algorithms.
$(\ek,\dk) \gets \EKeyGen(\parm)$ generates the encryption-decryption key
pair, algorithm $\Ec \gets \EEnc(\ek,\msg)$ encrypts message \msg with
encryption key \ek, producing ciphertext \Ec, and $\msg/\bot \gets \EDec(\dk,
\Ec)$ decrypts ciphertexts using decryption key \dk. We rely on IND-CCA
public-key encryption schemes.

@@

\paragraph{Non-Interactive Zero-Knowledge.} %
We use non-interactive zero-knowledge proofs of knowledge (NIZK), in the CRS
model. Informally, a NIZK scheme over an NP relation \NIZKRel is defined as a
tuple ($\NIZKSetupRel$,$\NIZKProveRel$,$\NIZKVerify^\NIZKRel$).
Algorithm $\NIZKcrs \gets \NIZKSetupRel(\secpar)$ produces the common
reference string \NIZKcrs. $\NIZKproof/\bot \gets \NIZKProveRel(\NIZKcrs,
\NIZKx,\NIZKw)$ creates a NIZK proof of knowledge of witness \NIZKw for \NIZKx
such that $(\NIZKw,\NIZKx) \in \NIZKRel$. $1/0 \gets \NIZKVerifyRel
(\NIZKcrs,\NIZKx,\NIZKproof)$ verifies the proof. Within NIZK systems, we
further need schemes that provide simulation extractability, which in a nutshell
means that no adversary can produce a proof from which we cannot extract a
witness, even after seeing polynomially many simulated proofs. To model
simulation extractable NIZKs, we further need algorithms \NIZKSimSetup,
\NIZKSim, and \NIZKExtract, that allow simulating proofs and extracting
witnesses. The properties we build on are completeness, soundness,
zero-knowledgeness, and simulation extractability.
